lab_notebook

### 2018-12-09 lab_notebook.Rmd
probability functions for itq and turfs

@@

#write.csv(f_b_itq, file = "f_b_itq.csv")
f_b_irights <- read_csv("data/f_b_irights.csv")

# get data frame that was
F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 22)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

@@

@@

Fixing upsie data
- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
- filter out just ones with itqs, create a column thats rights based fisherse and make it one
- filter out specifics of itq
- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
- make nas zero
-redo kobe plot with this data
- also cut off at 5

@@

#write.csv(f_b_itq, file = "f_b_itq.csv")
f_b_irights <- read_csv("data/f_b_irights.csv")

# get data frame that was
F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 22)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

>>>>

2. From upside sorts KOBE: ITQ versus non ITQ and the size of dot is the catch
#this is all the data we have, make the same ones with only certain years and such

@@

f_b_itq <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

#turf == TRUE ~ "2",
#write.csv(f_b_itq, file = "f_b_itq.csv")
#f_b_irights <- read_csv("data/f_b_irights.csv")
#this was when i couldn't figure out how to do the if then statement in R

#F_B_graph <- ggplot(data = f_b_irights, aes( x=BvBmsy, y=FvFmsy, colour= i_rights, size = catch ))+

# get data frame that was
F_B_graph <- ggplot(data = f_b_itq, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

@@

1.	From upside want to know the catch in ITQ versus non ITQ for most recent year
corbet data only goes up until 2012 
```{r}

ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012")

ITQ_projection_2016 <- ITQ_projection %>%
  filter(Year == "2016") %>%
  select(IdOrig, Country)

itq_2016_rightsbasedTRUE <- filter(itq_2016_updated, rightsbased == "1")

itq_2016_rightsbasedTURF <- filter(itq_2016_updated, rightsbased == "2")

sum(itq_2016_rightsbasedTURF$Catch, na.rm = TRUE)
#1505000

updating projection datapast 2012  with the 2012 itq fisheries
```{r}
ITQ_projection <- readRDS("data/ITQ_projection.rds")

f_b_itq_countries <- ITQ_projection %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch", "Year", "Country", "IdOrig") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

countries_itq_2012 <- f_b_itq_countries %>%
  select (Country, rightsbased, Year, IdOrig, Catch) %>%
  filter(Year == "2012")

ITQ_projection_past2012 <- ITQ_projection %>%
  filter(Year > 2012)

ITQ_projection_past2012UPDATED <- join(ITQ_projection_past2012, countries_itq_2012, by = c("Country", "Year", "IdOrig"), type = "full" )

ITQ_projection_pre2012 <- ITQ_projection %>%
  filter(Year <= 2012)

ITQ_projection_updated <- join(ITQ_projection_past2012UPDATED,ITQ_projection_pre2012, by = c("Country", "Year", "IdOrig"), type = "full")

#saveRDS(ITQ_projection_updated, "ITQ_projection_updated.rds")

ITQ_projection_updated <- readRDS("data/ITQ_projection_updated.rds")

f_b_itq_updated <- ITQ_projection_updated %>%
  select("BvBmsy", "FvFmsy", "itq", "iq", "ivq", "turf", "Catch") %>%
  filter( itq != "NA", iq != "NA", ivq != "NA") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

F_B_graph_updated <- ggplot(data = f_b_itq_updated, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(-1, 5)+
  xlim(-.3, 3)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))

#F_B_graph
ggplotly(F_B_graph_updated)

###Did this chunck before figured out how to do if/then statements in r

@@

Fixing upside data
- take ITQ projection an filter it down to idorig, year, BvBmsy", "FvFmsy", "itq", "iq", "ivq"
- filter out just ones with itqs, create a column thats rights based fisherse and make it one
- filter out specifics of itq
- merge/join that data with the countries_itq2012 with country, idorig, and rihgts based
- make nas zero
-redo kobe plot with this data
- also cut off at 5

#this was from before figured out if then statement

ITQ_projection <- readRDS("data/ITQ_projection.rds")

itq_selected <- ITQ_projection %>%
  select(IdOrig,Country, Year, BvBmsy, FvFmsy, itq, iq, ivq) %>%
  filter(itq != "NA" | iq != "NA" | ivq != "NA")

itq_selected$rightsbased <- 1

itq_selected_2 <- select(itq_selected,Country, IdOrig, Year, rightsbased)

itq_new_join <- join(itq_selected_2, countries_itq_2012, by = c(Country, IdOrig, Year), type = "full")

##not using this anymore

@@
